On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-07-30 manuscripts/IEEE/final_submission.tex
no exam jams

\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.

>>>>

%\textbf{Acknowledgement.} We thank Fritz Sommer and Darren Rhea for early thoughts, and Ian Morris for posting \eqref{eqdim} online.

\textbf{Acknowledgement.} We thank Fritz Sommer for turning our attention to the dictionary learning problem and Darren Rhea for sharing early explorations. We also thank Ian Morris for posting a reference to his proof of \eqref{eqdim} online at Stack Exchange. Finally, we thank Bizzyskillet (www.soundcloud.com/bizzyskillet) for the “No-Exam Jams”, to which many of our proofs were designed and constructed.}
